A Particular Appetite: Cosmological Hydrodynamic Simulations of Preferential Accretion in the Supermassive Black Holes of Milky Way Size Galaxies

### 2016-03-31 ms.tex
Added the results section

The galaxy, h258, is characterized by an active merger history including a major merger at z=1. Figure \ref{h258piefrac} depicts the fractions of total gas in the galaxy (a) and the SMBH (b) at z=0 differentiated by their method of entrance. The galaxy has a reservoir nearly half comprised of gas entering the galaxy through unshocked, smooth accretion (48 \%), with 39 \% of the gas entering through mergers. The smallest fractions of the total gas are comprised of shocked gas (9 \%) and ``early''gas that was maintained during the formation of the galaxy makes up the final, smallest fraction (4 \%). Unlike the galaxy, nearly 65 \% of the gas accreted by the central SMBH was gas accreted via mergers, while only a quarter (26 \%) is comprised of unshocked, smoothly accreted gas. Shocked gas makes up the last 9 \% of total gas entering the SMBH, along with a negligible (<1\%) amount of``early'' gas. This results shows explicitly that the SMBH more readily accretes gas gained through mergers. This is contrary to previous results of \cite{Bellovary2013}.

We examine the angular momentum of the gas at the moment it enters the galaxy for clues to the understand the ready accretion of merger accreted gas. (Figure \ref{h258_angmom_cumudist}) A cumulative distribution of angular momentum of the entering gas, differentiated based on method of entrance into the galaxy, shows that gas entering the SMBH (dashed lines) has an overall lower angular momentum whether it enters via unshocked smooth accretion, becomes shocked upon entry, or enters through a galaxy merger (blue, red, green, respectively).
\citep{Bellovary2013} found a \textit{slight} preference for gas of a lower angular momentum to enter the SMBH By examining the angular momentum of the gas accreted onto the SMBH at the moment it enters the halo, we were able to determine that a significant preference exists for gas with lower angular momentum to enter the SMBH. The gas attained through mergers tends to enter the halo with a lower angular momentum; this may explain the SMBH's preference for merger gas.

@@

Our quiescent galaxy, h277, was characterized by few mergers in its past, its final major merger occuring around z$\sim$3. Similar to Bellovary et. al. 2013 study, which found SMBH accretion in high mass, high redshift galaxies mirror their hosts in terms of accretion, h277's SMBH accretes a similar fraction of each type of gas, comparable to its host galaxy. (Figure \ref{h277piefrac}) So, h277, unlike the active h258, found no preference for the SMBH to prefer any one kind of gas in its accretion. Like the SMBH in the previous study, the same fraction of gas entering the halo would then be accreted onto the SMBH. (The gas enters a sort of reservoir and enters the SMBH somewhat uniformly.)  As these SMBHs are similar in size and appearance at z=0, this indicates that the varying histories of these simulations plays a role in the evolution of these galaxies and their central SMBH.

@@

[Still need to write]
Look I am adding some text. #gittest

@@

\begin{figure}
\centerline{\resizebox{0.55\hsize}{!}{\includegraphics[angle=0]{PIE_h258galgasfrac_noexplode_realcolors}}}
\centerline{\resizebox{0.55\hsize}{!}{\includegraphics[angle=0]{PIE_h258bhgasfrac_noexplode_realcolors}}}
\caption[]{Gas fractions of the gas particles accreted in h258 by the main halo (above) and the SMBH (below), distinguished by type. Blue, green, and red distinguish gas gained through unshocked gas, gained through mergers, and gas shocked upon entry, respectively. Yellow indicates gas that existed within the main halo upon formation; this ``early'' gas is negligible (<1 \%) within the SMBH.}
\label{h258piefrac} 
\end{figure}

@@

\begin{figure}
\centerline{\resizebox{0.75\hsize}{!}{\includegraphics[angle=0]{h277_angmom_cumudist_wrongaxis}}}
\caption[]{ Cumulative distribution of angular momentum of the gas particles accreted onto h277.  Gas particles accreted onto the main halo (solid lines) and central black hole (dashed lines). The green, blue, and red lines indicate clumpy, unshocked, and shocked gas, respectively.}
\label{h277angmom} 
\end{figure}

>>>>

The galaxy, h258, is characterized by an active merger history including a major merger at z=1. The merger can be clearly seen affecting the cumulative black hole mass \ref{h258allmassgas} as well as the gas fractions within the both the SMBH and galaxy \ref{h258numfrac}. 
Though Figure \ref{h258allmassgas} shows that the primary source of mass gain at high redshifts is through mergers with other black holes, there is clearly a significant increase in the amount of gas adding to the mass of the SMBH at z $\sim$ 1.

Similarly, Figure \ref{h258numfrac} shows that unshocked gas (blue) makes up the majority of gas entering the galaxy (solid lines) at early times; nevertheless, around the time of ther merger (z $\sim$ 1) a marked change occurs in the gas fractions within the black hole (dashed lines) where merger gas (green) becomes the main component of total gas.

igure \ref{h258piefrac} depicts the fractions of total gas in the galaxy (a) and the SMBH (b) at z=0 again differentiated by their method of entrance. The galaxy has a reservoir nearly half comprised of gas entering the galaxy through unshocked, smooth accretion (48 \%), with 39 \% of the gas entering through mergers. The smallest fractions of the total gas are comprised of shocked gas (9 \%) and ``early''gas that was maintained during the formation of the galaxy makes up the final, smallest fraction (4 \%). Unlike the galaxy, nearly 65 \% of the gas accreted by the central SMBH was gas accreted via mergers, while only a quarter (26 \%) is comprised of unshocked, smoothly accreted gas. Shocked gas makes up the last 9 \% of total gas entering the SMBH, along with a negligible (<1\%) amount of``early'' gas. This results shows explicitly that the SMBH more readily accretes gas gained through mergers. This is contrary to previous results of \cite{Bellovary2013}.

We examine the angular momentum of the gas at the moment it enters the galaxy for clues to the understand the ready accretion of merger accreted gas. (Figure \ref{h258_angmom_cumudist}) A cumulative distribution of angular momentum of the entering gas, differentiated based on method of entrance into the galaxy, shows that gas entering the SMBH (dashed lines) has an overall lower angular momentum than gas entering galaxy (solid lines). This is true whether the enters via unshocked smooth accretion, becomes shocked upon entry, or enters through a galaxy merger (blue, red, green, respectively).

\citep{Bellovary2013} found a \textit{slight} preference for gas of a lower angular momentum to enter the SMBH By examining the angular momentum of the gas accreted onto the SMBH at the moment it enters the halo, we were able to determine that a significant preference exists for gas with lower angular momentum to enter the SMBH. The gas attained through mergers tends to enter the halo with a lower angular momentum; this may explain the SMBH's preference for merger gas.

@@

Our quiescent galaxy, h277, was characterized by few mergers in its past, its final major merger occuring around z $\sim$ 3. This merger is visible in Figure \ref{h277allmassgas}, though more subtle than the influx of gas in h258. In h277, gas seemed to be gained at a more steady rate and even at fairly high redshifts comprises a larger portion of the black holes total mass than seen in the previous galaxy. The gas fractions (Figure \ref{h277numfrac}) in the galaxy (solid lines) and SMBH (dashed lines) are also markedly different than that of the active galaxy. While it appears neither merger-gained or unshocked gas (green and blue,respectively) particularly dominates at higher redshifts in the galaxy, merger gas becomes prominent in the SMBH at times when mergers occur implying some physical process allowing merger gas to readily fuel black hole growth. Though, it is important to note that by z $\sim$ 0, smoothly accreted, unshocked gas dominates in both the SMBH and host galaxy.

This results can be more clearly seen in Figure \ref{h277piefrac}. Similar to Bellovary et. al. 2013 study, which found SMBH accretion in high mass, high redshift galaxies mirror their hosts in terms of accretion, h277's SMBH accretes a similar fraction of each type of gas, comparable to its host galaxy. Smoothly accreted, unshocked gas represents about half of the total gas in both the SMBH and the galaxy. Merger-gained gas also maintains about 30\% of both. There is an increase in the shocked gas accreted by the SMBH, but this may be due to supernova contamination. So by present day, h277, unlike the active h258, found no strong preference for the SMBH to prefer any one kind of gas in its accretion. Like the SMBH in the previous study \pcite{Bellovary2013}, the same fraction of gas entering the halo would then be accreted onto the SMBH.

As in the previous case, we examined the angular momentum of all the gas particles accreted by the SMBH and host galaxy at the moment of entry. \ref{h277angmom} It is immediately apparent that the merger gas accreted by both the black hole and its host has a lower angular momentum overall than the smoothly accreted gas; however, unlike we found in h258, the h277 galaxy accretes gas with lower angular momentum than that of its SMBH.

As h277 and h258 are similar in size and appearance at z=0, these differences indicate that the varying histories of these simulations plays a role in the evolution of these galaxies and their central SMBH.

@@

[Still need to write]

@@

\begin{figure}
\centerline{\resizebox{0.55\hsize}{!}{\includegraphics[angle=0]{PIE_h258galgasfrac_noexplode_realcolors}}}
\centerline{\resizebox{0.55\hsize}{!}{\includegraphics[angle=0]{PIE_h258bhgasfrac_noexplode_realcolors}}}
\caption[]{Gas fractions of the gas particles accreted in h258 by the main halo (above) and the SMBH (below), distinguished by type. Blue, green, and red distinguish gas gained through unshocked gas, gained through mergers, and gas shocked upon entry, respectively. Yellow indicates gas that existed within the main halo upon formation; this ``early'' gas is negligible (\< 1 \%) within the SMBH.}
\label{h258piefrac} 
\end{figure}

@@

\begin{figure}
\centerline{\resizebox{0.75\hsize}{!}{\includegraphics[angle=0]{angmom_cumudist_cumu_512}}}
\caption[]{ Cumulative distribution of angular momentum of the gas particles accreted onto h277.  Gas particles accreted onto the main halo (solid lines) and central black hole (dashed lines). The green, blue, and red lines indicate clumpy, unshocked, and shocked gas, respectively.}
\label{h277angmom} 
\end{figure}
